\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-28 syntactic-example.tex
\coloneqq

  \begin{minipage}[t]{0.4\linewidth}
\begin{align*}
  "Osig" &:= \goodWSig{\cdot}{w^+\ w\cdot\ \top\ \bot}{1} \\
  "sig"_1 &:= \goodSig{\cdot}{\nu^+ \ \nu\cdot  \ (\bW \ "Osig"[\pi_1])}{1}  \\
  "obj"_1 &:= \goodTerm{\cdot}{\mu^+ \ \mu\cdot \ {id_s} \ *}{\cL"sig"_1}\\
  \cC"sig"_1 &= \goodType{\cdot}{\Sigma \ \top \ (\bW \ "Osig"[\pi_1]) }{} \\
  "sig"_2 &:=  \goodSig{\cdot}{\nu^+ \ "sig"_1 \ {id_s} \ El ("W" ("pjr" \ \pi_2))}{2} \\ 
  "O"_1 &:= {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ and thus }  \goodTerm{\cdot, \cC"sig"_1}{"O"_1}{El ("W" ("pjr" \pi_2))} \\
  "obj"_2 &:= \goodTerm{\cdot}{\mu^+ \ "obj"_1 \ "O"_1}{\cL"sig"_2} \\
  "sig"_2' &:= \goodType{\cdot}{\Sigma (\Sigma \top \cU)El ("pjr" \pi_2)}{} \\ 
  \cC"sig"_2 &= \goodType{\cdot}{\Sigma (\Sigma \top (\bW \ "Osig"[\pi_1]))El \ W("pjr" \pi_2) }{} \\ 
  "sl"_1 &:= ((*, "W" ("pjr" ("pjl" \pi_2)) ), "pjr" \pi_2) \\ 
  & \text{ and thus }  \goodSeal{\cdot}{"sl"_1}{"sig"_2}{"sig"_2'} \\
  "pN"_1 &:= \goodType{\cdot, "sig"_2'}{El ("pjr" ("pjl" \pi_2)) * El ("pjr" ("pjl" \pi_2))}{} \\
  "handler"_1 & := \goodTerm{\cdot, "sig"_2'}{\_}{\cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)} \\
  "sig"_3 &:= \goodSig{\cdot}{\nu^+ "sig"_2 \{"sl"_1\} \ \cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)}{3} \\ 
  "obj"_3 &: \goodTerm{\cdot}{\mu^+~"obj"_2~"handler"_1}{\cL"sig"_3}\\
  "predT" := (\Pi & \ El ("W"("pjr" ("pjl"^2 \pi_2))) \\  
  & (El ("W" ("pjr" ("pjl"^2  \pi_2)))[\pi_1])) \\
  "pred"_1 & := \goodTerm{\cdot, \cC "sig"_3}{\lambda ("Wrec" \_)}{"predT"} \\ 
  "sig"_4 &:= \nu^+ \ "sig"_3 \ \{id_s\} \ "predT" \\ 
  "obj"_4 &: \goodTerm{\cdot}{\mu^+~"obj"_3~"pred"_1}{\cL"sig"_4}\\
  "sl"_4 &:= \goodSeal{\cdot}{\_}{"sig"_4}{"sig"_4'} \\
  "pN"_2 &:= \goodType{\cdot, "sig"_4'}{El ("pjr" ("pjl" \pi_2)) * El ("pjr" ("pjl" \pi_2))}{}
\end{align*}
\end{minipage}%
\begin{minipage}[t]{0.4\linewidth}
\begin{align*}
  "sig"_5 &:= \nu^+ \ "sig"_4 \ \{"sl"_4\} \  "pN"_2 \\ 
  "obj"_5 &: \goodTerm{\cdot}{\mu^+~"obj"_4~\_}{\cL"sig"_4}\\
  \\ 
  \text{Here we}&\text{ start to construct Family } "A"_2 \\ 
  "Nsig" &:= \goodWSig{\cdot}{w+ \ \top \ \bot \  "Osig"}{1} \\ 
  "sig"_{11} &:= \goodSig{\cdot}{\nu^+ \ \nu\cdot  \ (\bW \ "Nsig"[\pi_1])}{1} \\
  "inh"_1 &:= \goodInh{\cdot}{"inhov" \  "inhid" \ *}{"sig"_1}{"sig"_{11}}\\
  "O"_2 &:= {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ but }  \goodTerm{\cdot, \cC"sig"_{11}}{"O"_2}{El ("W" ("pjr" \pi_2))} \\
  "sig"_{21} &:= \nu^+ \ "sig"_{11} \ \{id_s\} (El (W (pjr p₂))) \\ 
  "inh"_2 &:= \goodInh{\cdot}{"inhov" \ "inh"_1 \ "O"_2}{"sig"_2}{"sig"_{21}}\\
  "S"_T := (\Pi & \ El ("W"("pjr"  ("pjl" \pi_2))) \\  
  & (El ("W" ("pjr" ("pjl"  \pi_2)))[\pi_1])) \\
  "sig"_{22} &:= \nu^+ \ "sig"_{21} \ \{id_s\} \ "S"_T \\ 
  "sig"_{21}' &:= \goodType{\cdot}{\Sigma (\Sigma \top \cU) (El ("pjr" \pi_2))}{} \\
  "sig"_{22}' &:= \Sigma "sig"_{21}' (\Pi \ El ("pjr"  ("pjl" \pi_2)) \  ...) \\
  "sl"_{22} &:= \goodSeal{\cdot}{\_}{"sig"_{22}}{"sig"_{22}'} \\ 
  "inh"_3 &:= \goodInh{\cdot}{\_}{"sig"_2}{"sig"_{22}} \\ 
  \uparrow^s &:= \goodTerm{\cdot, "sig"_{22}'}{\_}{"sig"_2'[\pi_1]} \\ 
  "pN"_3 &:= "pN"_1[(\pi_1, \uparrow^s)] \\ 
\end{align*}
  \end{minipage}

  \begin{minipage}{0.8\linewidth}
    \centering
    \begin{align*}
      "inh"_{in0} &:= \goodInh{\cdot, "sig"_{22}'}{"inhid"}{(\nu^+ \ \nu\cdot \ ("pN"_1[\pi_1]))[(\pi_1, \uparrow^s)]}{(\nu^+ \cdot ("pN"_3[\pi_1]))} \\
      "inh"_{in} &:= \goodInh{\cdot , "sig"_{22}'}{\_}{(\nu^+ \ \nu\cdot \ "pN"_1[\pi_1])[(\pi_1, \uparrow^s)]}{(\nu^+ \ \cdot \ ("pN"_3[\pi_1]) \ \{id_s\} (\Pi "pN"_3 ("pN"_3[\pi_1])) )[\pi_1]}\\
      "sig"_{31} &:=  \nu^+ \ "sig"_{22} \ {"sl"_{22}}\  \cL(\nu^+ \cdot ("pN"_3[\pi_1])  (\Pi "pN"_3 ("pN"_3[\pi_1]))[\pi_1]) \\ 
      "inh"_4 &:= \goodInh{\cdot}{"inhnest" \ "inh"_3 \uparrow^s "inh"_{in}}{"sig"_3}{"sig"_{31}} \\
      "sig"_{41} &:= {\nu^+ \ "sig"_{31} \ (\Pi (El ("W" ("pjr" ("pjl"^4 \pi_2)))) (El ("W" ("pjr" ("pjl"^4 \pi_2))))[\pi_1])} \\ 
      "inh"_5 &:= \goodInh{\cdot}{inhov \ \_}{"sig"_4}{"sig"_{41}} \\ 
      "sl"_{41} &:= \goodSeal{\cdot}{\_}{"sig"_{41}}{"sig"_{41}'} \\ 
      \uparrow^s_2 &:= \goodTerm{\cdot, "sig"_{41}}{\_}{"sig"_4'[\pi_1]} \\ 
      "inh"_6 &:= \goodInh{\cdot}{"inhinh" \ "inh"_5 \ \uparrow^s_2}{"sig"_5}{(\nu^+ \ "sig"_{41} \{"sl"_{41}\} \ "pN"_2[(\pi_1, \uparrow^s_2)])}
    \end{align*}  
  \end{minipage}
  \caption{Detailed Construction}\label{fig:example-construction}
\end{figure}

>>>>

  \begin{minipage}[t]{0.4\linewidth}
  \small
\begin{align*}
  "Osig" &\coloneqq \goodWSig{\cdot}{w^+\ w\cdot\ \top\ \bot}{1} \\
  "sig"_1 &\coloneqq \goodSig{\cdot}{\nu^+ \ \nu\cdot  \ (\bW \ "Osig"[\pi_1])}{1}  \\
  "obj"_1 &\coloneqq \goodTerm{\cdot}{\mu^+ \ \mu\cdot \ {id_s} \ *}{\cL"sig"_1}\\
  \cC"sig"_1 &= \goodType{\cdot}{\Sigma \ \top \ (\bW \ "Osig"[\pi_1]) }{} \\
  "sig"_2 &\coloneqq  \goodSig{\cdot}{\nu^+ \ "sig"_1 \ {id_s} \ El ("W" ("pjr" \ \pi_2))}{2} \\ 
  "O"_1 &\coloneqq {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ and thus }  \goodTerm{\cdot, \cC"sig"_1}{"O"_1}{El ("W" ("pjr" \pi_2))} \\
  "obj"_2 &\coloneqq \goodTerm{\cdot}{\mu^+ \ "obj"_1 \ "O"_1}{\cL"sig"_2} \\
  "sig"_2' &\coloneqq \goodType{\cdot}{\Sigma (\Sigma \top \cU)El ("pjr" \pi_2)}{} \\ 
  \cC"sig"_2 &\coloneqq \goodType{\cdot}{\Sigma (\Sigma \top (\bW \ "Osig"[\pi_1]))El \ W("pjr" \pi_2) }{} \\ 
  "sl"_1 &\coloneqq ((*, "W" ("pjr" ("pjl" \pi_2)) ), "pjr" \pi_2) \\ 
  & \text{ and thus }  \goodSeal{\cdot}{"sl"_1}{"sig"_2}{"sig"_2'} \\
  "pN"_1 &\coloneqq \goodType{\cdot, "sig"_2'}{El ("pjr" ("pjl" \pi_2)) * El ("pjr" ("pjl" \pi_2))}{} \\
  "handler"_1 &\coloneqq \goodTerm{\cdot, "sig"_2'}{\_}{\cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)} \\
  "sig"_3 &\coloneqq \goodSig{\cdot}{\nu^+ "sig"_2 \{"sl"_1\} \ \cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)}{3} \\ 
  "obj"_3 &\coloneqq \goodTerm{\cdot}{\mu^+~"obj"_2~"handler"_1}{\cL"sig"_3}\\
  "predT" &\coloneqq \Pi \ El ("W"("pjr" ("pjl"^2 \pi_2)))\ El ("W" ("pjr" ("pjl"^2  \pi_2)))[\pi_1] \\
  "pred"_1 &\coloneqq \goodTerm{\cdot, \cC "sig"_3}{\lambda ("Wrec" \_)}{"predT"} \\ 
  "sig"_4 &\coloneqq \nu^+ \ "sig"_3 \ \{id_s\} \ "predT" \\ 
  "obj"_4 &\coloneqq \goodTerm{\cdot}{\mu^+~"obj"_3~"pred"_1}{\cL"sig"_4}\\
  "sl"_4 &\coloneqq \goodSeal{\cdot}{\_}{"sig"_4}{"sig"_4'} \\
  "pN"_2 &\coloneqq \goodType{\cdot, "sig"_4'}{El ("pjr" ("pjl" \pi_2)) * El ("pjr" ("pjl" \pi_2))}{}
\end{align*}
\end{minipage}%
\begin{minipage}[t]{0.4\linewidth}
\begin{align*}
  "sig"_5 &\coloneqq \nu^+ \ "sig"_4 \ \{"sl"_4\} \  "pN"_2 \\ 
  "obj"_5 &: \goodTerm{\cdot}{\mu^+~"obj"_4~\_}{\cL"sig"_4}\\
  \\ 
  \text{Here we}&\text{ start to construct Family } "A"_2 \\ 
  "Nsig" &\coloneqq \goodWSig{\cdot}{w+ \ \top \ \bot \  "Osig"}{1} \\ 
  "sig"_{11} &\coloneqq \goodSig{\cdot}{\nu^+ \ \nu\cdot  \ (\bW \ "Nsig"[\pi_1])}{1} \\
  "inh"_1 &\coloneqq \goodInh{\cdot}{"inhov" \  "inhid" \ *}{"sig"_1}{"sig"_{11}}\\
  "O"_2 &\coloneqq {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ but }  \goodTerm{\cdot, \cC"sig"_{11}}{"O"_2}{El ("W" ("pjr" \pi_2))} \\
  "sig"_{21} &\coloneqq \nu^+ \ "sig"_{11} \ \{id_s\} (El (W (pjr p₂))) \\ 
  "inh"_2 &\coloneqq \goodInh{\cdot}{"inhov" \ "inh"_1 \ "O"_2}{"sig"_2}{"sig"_{21}}\\
  "S"_T := (\Pi & \ El ("W"("pjr"  ("pjl" \pi_2))) \\  
  & (El ("W" ("pjr" ("pjl"  \pi_2)))[\pi_1])) \\
  "sig"_{22} &\coloneqq \nu^+ \ "sig"_{21} \ \{id_s\} \ "S"_T \\ 
  "sig"_{21}' &\coloneqq \goodType{\cdot}{\Sigma (\Sigma \top \cU) (El ("pjr" \pi_2))}{} \\
  "sig"_{22}' &\coloneqq \Sigma "sig"_{21}' (\Pi \ El ("pjr"  ("pjl" \pi_2)) \  ...) \\
  "sl"_{22} &\coloneqq \goodSeal{\cdot}{\_}{"sig"_{22}}{"sig"_{22}'} \\ 
  "inh"_3 &\coloneqq \goodInh{\cdot}{\_}{"sig"_2}{"sig"_{22}} \\ 
  \uparrow^s &\coloneqq \goodTerm{\cdot, "sig"_{22}'}{\_}{"sig"_2'[\pi_1]} \\ 
  "pN"_3 &\coloneqq "pN"_1[(\pi_1, \uparrow^s)] \\ 
\end{align*}
  \end{minipage}

  \begin{minipage}{0.8\linewidth}
    \centering
    \begin{align*}
      "inh"_{in0} &\coloneqq \goodInh{\cdot, "sig"_{22}'}{"inhid"}{(\nu^+ \ \nu\cdot \ ("pN"_1[\pi_1]))[(\pi_1, \uparrow^s)]}{(\nu^+ \cdot ("pN"_3[\pi_1]))} \\
      "inh"_{in} &\coloneqq \goodInh{\cdot , "sig"_{22}'}{\_}{(\nu^+ \ \nu\cdot \ "pN"_1[\pi_1])[(\pi_1, \uparrow^s)]}{(\nu^+ \ \cdot \ ("pN"_3[\pi_1]) \ \{id_s\} (\Pi "pN"_3 ("pN"_3[\pi_1])) )[\pi_1]}\\
      "sig"_{31} &\coloneqq  \nu^+ \ "sig"_{22} \ {"sl"_{22}}\  \cL(\nu^+ \cdot ("pN"_3[\pi_1])  (\Pi "pN"_3 ("pN"_3[\pi_1]))[\pi_1]) \\ 
      "inh"_4 &\coloneqq \goodInh{\cdot}{"inhnest" \ "inh"_3 \uparrow^s "inh"_{in}}{"sig"_3}{"sig"_{31}} \\
      "sig"_{41} &\coloneqq {\nu^+ \ "sig"_{31} \ (\Pi (El ("W" ("pjr" ("pjl"^4 \pi_2)))) (El ("W" ("pjr" ("pjl"^4 \pi_2))))[\pi_1])} \\ 
      "inh"_5 &\coloneqq \goodInh{\cdot}{inhov \ \_}{"sig"_4}{"sig"_{41}} \\ 
      "sl"_{41} &\coloneqq \goodSeal{\cdot}{\_}{"sig"_{41}}{"sig"_{41}'} \\ 
      \uparrow^s_2 &\coloneqq \goodTerm{\cdot, "sig"_{41}}{\_}{"sig"_4'[\pi_1]} \\ 
      "inh"_6 &\coloneqq \goodInh{\cdot}{"inhinh" \ "inh"_5 \ \uparrow^s_2}{"sig"_5}{(\nu^+ \ "sig"_{41} \{"sl"_{41}\} \ "pN"_2[(\pi_1, \uparrow^s_2)])}
    \end{align*}  
  \end{minipage}
  \caption{Detailed Construction}\label{fig:example-construction}
\end{figure}
